
---
title: "Final Project: GW Tobacco History Completeness Pilot Dashboard | PUBH 6199: Visualizing Data with R"

author:
  - name: Sora Ely; Ashlan Jackson
    affiliation: George Washington University
date: "2025-06-26"
format: 
  html:
    toc: true
    toc-location: right
    code-fold: true
    self-contained: true
theme: flatly
mainfont: "Arial"
fontsize: 11pt
execute:
  echo: true
  warning: false
  message: false
output-dir: docs
params:
  number: 6
  purpose: "Final project for PUBH 6199: Visualizing Data with R"
---
```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.path = "figs/",
    fig.width = 7.252,
    fig.height = 4,
    comment = "#>",
    fig.retina = 3
)
```

"Accompanying your visualizations, you should also include a write-up around 500-1000 words that consists of an introduction, research questions, data sources, data wrangling, data visualizations, findings, and conclusion."


## Introduction
_In this project, our team was investigating the clinical departments that acquired a complete tobacco history and our team was interested in which departments needed to improve their data collection._


## Research Question
@SORA

## Data Sources
@SORA
_Describe your data source(s), including where it came from, the key variables, and any pre-processing steps._


## Data Wrangling

```{r}
#| label: load packages and data

#| eval: true
install.packages("shiny")
install.packages("ggrepel")
install.packages("viridis")

#| output: FALSE

library(viridisLite)
library(viridis)
tobacco_data_weekly_modified <- read_csv("data/tobacco_data_weeklymodified.csv")

tobacco_data_monthly_moified <- read_csv("data/tobacco_data_monthlymodified.csv")


```   
## Data Visualizations

## Visualization 1: "Highest and Lowest Departments with Complete Tobacco History (Weekly)"
_This plot shows the departments with the highest and lowest percentages of a complete tobacco history and plot will help providers diagnoses lung issues sooner._

===========



```{r}

library(ggplot2)
library(dplyr)
library(ggrepel)
library(viridis)

summary_groups <- tobacco_data_weekly_modified %>%
  filter(!group %in% c("Pilot", "Non-Pilot")) %>%
  filter(week_num == max(week_num)) %>%
  group_by(group) %>%
  summarize(final_value = max(percent_complete, na.rm = TRUE)) %>%
  arrange(desc(final_value))

top_groups <- summary_groups %>% slice_head(n = 2) %>% pull(group)
bottom_groups <- summary_groups %>% slice_tail(n = 2) %>% pull(group)
highlight_groups <- c(top_groups, bottom_groups)

highlight_colors <- c(
  setNames(rep("steelblue", 2), top_groups),
  setNames(rep("firebrick", 2), bottom_groups),
  "Other" = "gray80"
)

ggplot(
  tobacco_data_weekly_modified %>%
    filter(!group %in% c("Pilot", "Non-Pilot")) %>%
    mutate(line_group = ifelse(group %in% highlight_groups, group, "Other")),
  aes(x = week_num, y = percent_complete, group = group)
) +
  geom_line(aes(color = line_group, size = line_group, alpha = line_group)) +
  geom_point(aes(color = line_group, alpha = line_group), size = 2) +
  geom_text_repel(
    data = tobacco_data_weekly_modified %>%
      filter(group %in% highlight_groups) %>%
      group_by(group) %>%
      filter(week_num == max(week_num)),
    aes(label = group, color = group),
    nudge_x = 0.3,
    hjust = 0,
    segment.color = NA,
    size = 4,
    show.legend = FALSE
  ) +
  scale_color_manual(values = highlight_colors) +
  scale_size_manual(values = c(setNames(rep(1.4, 4), highlight_groups), "Other" = 0.6)) +
  scale_alpha_manual(values = c(setNames(rep(1, 4), highlight_groups), "Other" = 0.3)) +
  scale_x_continuous(
    breaks = unique(tobacco_data_weekly_modified$week_num),
    labels = paste("Week", unique(tobacco_data_weekly_modified$week_num)),
    expand = expansion(mult = c(0.05, 0.2))
  ) +
  labs(
    title = "Highest and Lowest Departments with Complete Tobacco History (Weekly)",
    x = "Week of",
    y = "Percent Complete"
  ) +
  theme_minimal() +  
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)  
  )

```


## Visualization 2: Highest and Lowest Departments Complete Tobacco History (Monthly)",

_This plot shows the departments with the highest and lowest percentages of a complete tobacco history by month and this plot will help providers diagnoses lung issues sooner.._


```{r}
library(ggplot2)
library(dplyr)
library(ggrepel)
library(viridis)

clean_data <- tobacco_data_monthly_moified %>%
  filter(!group %in% c("Pilot", "Non-Pilot", "Geriatrics (Ingleside)"))

summary_groups <- clean_data %>%
  filter(month_num == max(month_num)) %>%
  group_by(group) %>%
  summarize(final_value = max(percent_complete, na.rm = TRUE)) %>%
  arrange(desc(final_value))

top_groups <- summary_groups %>% slice_head(n = 2) %>% pull(group)
bottom_groups <- summary_groups %>% slice_tail(n = 2) %>% pull(group)
highlight_groups <- c(top_groups, bottom_groups)

highlight_colors <- c(
  setNames(rep("steelblue", 2), top_groups),
  setNames(rep("firebrick", 2), bottom_groups),
  "Other" = "gray80"
)

plot_data <- clean_data %>%
  mutate(line_group = ifelse(group %in% highlight_groups, group, "Other"))

ggplot(plot_data, aes(x = month_num, y = percent_complete, group = group)) +
  geom_line(aes(color = line_group, size = line_group, alpha = line_group)) +
  geom_point(aes(color = line_group, alpha = line_group), size = 2) +
  geom_text_repel(
    data = plot_data %>%
      filter(group %in% highlight_groups) %>%
      group_by(group) %>%
      filter(month_num == max(month_num)),
    aes(label = group, color = group),
    nudge_x = 0.3,
    hjust = 0,
    segment.color = NA,
    size = 4,
    show.legend = FALSE
  ) +
  scale_color_manual(values = highlight_colors) +
  scale_size_manual(values = c(setNames(rep(1.4, 4), highlight_groups), "Other" = 0.6)) +
  scale_alpha_manual(values = c(setNames(rep(1, 4), highlight_groups), "Other" = 0.3)) +
  scale_x_continuous(
    breaks = 1:12,
    labels = month.abb[1:12], 
    expand = expansion(mult = c(0.05, 0.2))
  ) +
  scale_y_continuous(
    limits = c(0, 1),
    labels = scales::percent_format(accuracy = 1)
  ) +
  labs(
    title = "Highest and Lowest Departments Complete Tobacco History (Monthly)",
    x = "Month",
    y = "Percent Complete"
  ) +
  theme_minimal() +
  theme(legend.position = "none")




```

## Shiny app: [Title Here]
@SORA
_If you choose to create a Shiny app, describe the app's purpose and functionality. Save your code inside the shiny-app/ folder, replace the URL below with your app's URL_

[Click here to open the interactive Shiny app](https://cindyhu.shinyapps.io/two-files-app/)


@SORA
_Summarize your key findings. What do your visualizations reveal?_

## Limitations
@SORA
_Discuss any data quality or design limitations._

## Conclusion
@SORA
_Wrap up your project with a takeaway message or next steps._


## References


1. Reference 1: Sora's Clinical Dataset. 
2. Reference 2
3. Reference 3

