---
title: "Final Project: GW Tobacco History Completeness Pilot Dashboard | PUBH 6199: Visualizing Data with R"
author:
  - name: Sora Ely; Ashlan Jackson
    affiliation: George Washington University
date: "2025-06-26"
editor: source
format: 
  html:
    toc: true
    toc-location: right
    code-fold: true
    self-contained: true
theme: flatly
mainfont: "Arial"
fontsize: 11pt
execute:
  echo: true
  warning: false
  message: false
output-dir: docs
params:
  number: 6
  purpose: "Final project for PUBH 6199: Visualizing Data with R"
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.path = "figs/",
    fig.width = 7.252,
    fig.height = 4,
    comment = "#>",
    fig.retina = 3
)
```

"Accompanying your visualizations, you should also include a write-up around 500-1000 words that consists of an introduction, research questions, data sources, data wrangling, data visualizations, findings, and conclusion."

## Introduction
@ASHLAN
_Briefly introduce your topic and research question._

## Research Question
@SORA

## Data Sources
@SORA
_Describe your data source(s), including where it came from, the key variables, and any pre-processing steps._

## Data Wrangling
@ASHLAN

```{r}
#| label: load packages and data
#| output: FALSE

library(tidyverse)
library(readr)
library(ggplot2)
library(shiny)
library(dplyr)

tobacco_hxcompl <- read_csv("data/tobacco_hxcompl.csv")
tobacco_dept <- read_csv("data/tobacco_dept.csv")
tobacco_staff <- read_csv("data/tobacco_staff.csv")
```   

## Data Visualizations

### Visualization 1: [Title Here]
@ASHLAN
_Describe what this plot shows, and why it's important._

```{r}
# your code here
```

### Visualization 2: [Title Here]
@ASHLAN
_Describe what this plot shows, and why it's important._

```{r}
# your code here
```

## Shiny app: [Title Here]
@SORA
_If you choose to create a Shiny app, describe the app's purpose and functionality. Save your code inside the shiny-app/ folder, replace the URL below with your app's URL_

[Click here to open the interactive Shiny app](https://cindyhu.shinyapps.io/two-files-app/)

## Interpretation
@SORA
_Summarize your key findings. What do your visualizations reveal?_

## Limitations
@SORA
_Discuss any data quality or design limitations._

## Conclusion
@SORA
_Wrap up your project with a takeaway message or next steps._

## References
@ASHLAN
_Include any references to data sources, packages, or literature you used. If your visualization design is inspired by someone else's work, cite those too._

1. Reference 1
2. Reference 2
3. Reference 3

