---
title: "scratch"
author:
  - name: Sora Ely, MD
    affiliation: George Washington University
date: "2025-06-15"
editor: source
format: 
  html:
    toc: true
    toc-location: right
    self-contained: true
theme: flatly
mainfont: "Arial"
fontsize: 11pt
execute:
  echo: true
  warning: false
  message: false
---

# to-do & requirements

## Prototype V1

[requirements]{.underline}{.smallcaps}

- [x] Data scraping and cleaning complete (using real world datasets, do not use R built-in data)

- [ ] At least one visualization already implemented, and draft for 2-3 more visualizations\
      -- Sora & Ashlan by Tues 06:00\
      - Sora = bar graph\
      - Ashlan = 1st line graph\

- [ ] If choosing R shiny app, rough webpage design and structure has to be done and implemented (placeholders for visualizations)\
      -- Sora to do Tues day before 16:00 1:1 meeting

~~- [ ] If choosing the other two options, clear outline and storytelling flow of the visualizations~~

- [ ] A README.md file in your GitHub repo that describes your project, how to view it, and any dependencies\
      -- Ashlan to make a draft by Tues 16:00 1:1 meeting\
      -- Sora to finalize Wed\

## Final data visualization product

Choose one from the following three options:

~~1. Same Question, Different Audiences (3 static charts): Create three visualizations that answer the same question, each designed for a different audience (e.g., general public, policy makers, technical experts).~~

~~2. Same Data, Different Questions (3 static charts): Use the same dataset to answer three different but related questions, each with its own focused visualization.~~

**3. Interactive Dashboard (1 app with 3 components): Build an interactive dashboard (e.g., with shiny, plotly, or similar tools) that includes at least three visual components for exploring your data dynamically.**

- [ ] 2nd line graph
      -- Ashlan by Tues night / Wed 06:00

- [ ] final webpage design & merging the graphs/Shiny apps
      -- Sora on Wed

- [ ] publish the Shiny app to Shiny.io
      -- Sora on Wed
    
- [ ] final push of the git project
      -- Sora by Thurs AM

## Final project presentation

- 10 minutes presentation
  - no slides :)

[Sora]{.underline}\
- [ ] What questions do you set out to answer with your visualizations? Why are they important?\
- [ ] Your data source and why they are chosen to answer your questions\
- [ ] Your intended audience\
[Ashlan]{.underline}\
- [ ] Two to three visualization design choices and how they help tell your story\
- [ ] Two to three takeaways from your visualizations that your audience should remember\
- [ ] Live demo of your visualizations (if applicable)\
[both]{.underline}\
- -- 30min before class Thurs and/or text\
- [ ] One to two challenges you encountered during this project and how you overcame them\
- [ ] One to two achievements you are proud of in this project\

- The presentation format is flexible, bring your laptop to present, and submit the presentation and final data visualization product as HW6


## bar graph (1)

1.  **% complete per time interval by pilot v non-pilot depts**\
    **= bar chart by aggregated pilot & non-pilot depts**\
    **for the selected time interval & number of intervals**\
    interactivity: select time interval (w v mo) & number of intervals (up to max available 12w/3mo) -- *will set the parameters for all 3 visualizations*\

```{r}
#| label: 0 - install packages
#| include: false
#| eval: false

install.packages(c('tidyverse',
                   'shiny',
                   'rsconnect',
                   'janitor',
                   # 'plotly', 
                   'scales'))

```

```{r}
#| label: setup

library(tidyverse) # includes: ggplot2, dplyr, tidyr, readr, purr, tibble, stringr, forcats, lubridate
library(shiny)
library(rsconnect)
library(janitor)
# library(bslib)
library(scales)

```

```{r}
#| label: import data

tobacco_init <- read_csv("C:/Users/sorae/Documents/RStudio/PUBH6199/hw6-bart/data/tobacco_data_init.csv")
glimpse(tobacco_init)

tobacco_clean <- read_csv("C:/Users/sorae/Documents/RStudio/PUBH6199/hw6-bart/data/tobacco_clean_AJ_filtered.csv")
glimpse(tobacco_clean)
```

```{r}

```

```{r}
#| label: bar graph 1 - work

tobacco_init |> 
  ggplot(aes(x = week, y = pcomplete, color = dept)) |> 
  

```